\label{chap:introduction}

Current fixed frame rate display technology, such as, DVI, HDMI, and DisplayPort\cite{BhowmikEtAl2012} are a commonly utilized, but limiting technology for high-speed IR display systems\cite{EjzakEtAl2016,LaVeignePrewarski2013}. These display technologies, designed for relatively low-speeds (generally 60Hz) incorporate a number of design decisions that limit the ability to utilize them effectively with IR emitter technology. Firstly, these technologies require custom designed synchronization solutions and hardware when utilized with multiple sources in-order to ensure correct synchronization because they are not designed to handle synchronization across multiple sources. Secondly, the fixed frame rate nature of technology imposes a static requirement on frame rate across all displayed frames increasing bandwidth requirements by requiring the same amount of data be sent for all frames regardless of what data changes. This necessarily means that maximum frame rate operation is limited by the resolution size of imagery due to bandwidth limitations.

In this paper, we propose an alternative to traditional display technology, a packetized display protocol (PDP) architecture capable of bridging the performance gap of ever increasing speed requirements of high speed projector systems. Our PDP architecture eschews with some of the assumptions found within traditional display technology in order to provide scalability, reduce bandwidth requirements, increase performance, ease synchronization burden, and provide a desirable set of features, such as, dynamic sub-window frame rates not found within current technology.

Our protocol architecture draws inspiration from the video processing field, where encoding schemes for video streaming represent a body of research that attempts to tackle a similar but more limited challenge\cite{BakarEtAl2017}. Some of these encoding schemes attempt to provide a variable frame rate for segments of the incoming stream through differencing algorithms, but also rely on compression\cite{CastilloEtAl2012} which reduces quality and introduce artifacts. In our case, we require lossless quality; and thus, cannot utilize these for our purposes. Instead, we seek to craft a lossless solution for the IRLED projector field that incorporates similar variable frame rate features.

The contributions of this paper are the architecture of a physical layer agnostic packetized display protocol with the following features (1) intelligent dynamic per-frame bandwidth utilization, (2) fine-grained control over frame transmission and synchronization, (3) dynamically changing intra-frame rates, and (4) a realized implementation of the protocol for use on array emitter technology.

The paper is divided into the following sections, design methodology, which discusses the rationale for PDP; abstract architecture, which discusses the overall abstract PDP architecture; packetized display protocol, which discusses the underlying PDP protocol; example scenario, which examines utilizing PDP within an example system; Implemented Architecture, which discusses an implementation of the protocol on an FPGA; Experimental Results, which shows sample data propagating through the system, and the conclusion, which discusses current and future work on PDP.
